 % -*- mode: LaTeX -*-
 % ... preamble ...
\documentclass[times,12pt,titlepage]{mstthesis}
\doublespacing
\usepackage[authoryear,sort]{natbib}
\usepackage{threeparttable}
\usepackage[final]{graphicx}
\usepackage{psfrag}
\usepackage{listings}
\usepackage{minted}
\usepackage[noprefix]{nomencl}
\usepackage{subcaption}
\usepackage{xr}
\usepackage{rotating}
\makenomenclature
\renewcommand{\nomgroup}[1]{
   \ifthenelse{\equal{#1}{A}}{\medskip \item \textbf{Roman}}{}%
   \ifthenelse{\equal{#1}{G}}{\medskip \item \textbf{Greek}}{}%
   \ifthenelse{\equal{#1}{S}}{\medskip \item \textbf{Subscripts}}{}%
}
\usepackage[nopar]{lipsum} % ... provides dummy text ...

 % ... end preamble ...

\begin{document}

 % ... specify: ms or phd ...

\begin{ThesisTitlePage}{phd}

 % ... title page info ...

\author{\MakeUppercase{Edward T. Norris}}

\thesistitle{\MakeUppercase{Discrete Ordinates CT Organ Dose Simulator (DOCTORS)}}

\department{Nuclear Engineering}

 % ... thesis committee ...

\ThesisAdvisor{Xin Liu}

 % If you have a co-advisor, enter the name in the
 % curly braces below and uncomment.
 % Otherwise, leave commented out.
 %\cothadviser{} % If you have 2 thesis advisers

%\memberone{Ayodeji Alajo}
%\membertwo{Hyoung Koo Lee}
%\memberthree{Gary Mueller}
%\memberfour{Fikret Ercal}

\ThesisCommittee{Ayodeji Alajo\\ Hyoung Koo Lee\\ Gary Mueller \\ Fikret Ercal}
%\memberfive{Prandtl}

 % ... Graduation date - NOT your submission date ...
\graddate{2017}

\end{ThesisTitlePage}
 % ... copyright page - true|false ...

\copyrightyear{2017}
\ThesisCopyrightPage{true}

 % ... front matter - thesis abstract ...

\begin{ThesisAbstract}
Computed tomography (CT) has become pervasive in medical diagnostics as improved imaging techniques and processing algorithms provide higher quality information to doctors. However, the exponentially increasing usage of CT has raised concerns regarding long term low-dose radiological risks. Currently, the dose to patients is computed using Monte Carlo methods and experimental tests. In other areas of radiation transport, deterministic codes have been shown to be much faster than Monte Carlo codes.

Currently, no deterministic methodology exists to automatically generate a spatially distributed dose profile from a CT voxel phantom. This work proposes a new code, Discrete Ordinate CT Organ Dose Simulator (DOCTORS) which utilizes a GPU accelerated raytracer and discrete ordinate solver to compute photon flux in the patient. The flux is then converted to dose.

The DOCTORS code was benchmarked against MCNP6 and found to have good qualitative agreement using both a water phantom and a realistic patient phantom. DOCTORS was also found to be much faster than MCNP6; MCNP takes hours to compute flux profiles that take less than a minute using DOCTORS.

A GPU algorithm was implemented that speeds up the DOCTORS code by a factor of up to nearly 40 for large problems. GPU acceleration was found to benefit smaller problems much less. Speedup was seen in both single precision and  double precision problems.

\end{ThesisAbstract}

 % ... front matter - thesis acknowledgements ...

\begin{ThesisAcknowledgment}
I would like to thank my adviser, Dr. Liu and all of the other graduate students for their continued support through my graduate career. I appreciate the time they spent helping me identifying problems and providing insight to solutions. I would also like to thank my committee members for their guidance throughout my PhD work.

I would also like to acknowledge the NRC for providing funding for my work. My work is supported by NRC grant NRC-HQ-13-G-38-0026.
\end{ThesisAcknowledgment}

\begin{ThesisFrontMatter}
\tableofcontents
\listoffigures
\listoftables
\listofsymbols
\end{ThesisFrontMatter}

\begin{ThesisBody}

 % ... introduction chapter ...
\ThesisBodyChapter{Introduction}\input{chapintro}
 % ... chapter ...
\ThesisBodyChapter{Literature Review}\input{chapbib}
 % ... chapter ...
\ThesisBodyChapter{Methods}\input{chapmeth}

\ThesisBodyChapter{Implementation}\input{chapimpl}
 % ... conclusions chapter ...

\ThesisBodyChapter{Results}\input{chapresults} 
 
\ThesisBodyChapter{Conclusions}\input{chapconc}

\end{ThesisBody}
 % ... appendix - specify number of appendix chapters ...

\begin{ThesisAppendix}{two}
\ThesisAppendixChapter{Legendre Polynomials and Spherical Harmonics}\input{appdx_a}

%\ThesisAppendixChapter{Code Listings}\input{appdx_b}

%\ThesisAppendixChapter{Benchmark Results}\input{appdx_c}

\end{ThesisAppendix}

 % ... references - comma separated list of bib files ...

\begin{ThesisBibliography}{BIBLIOGRAPHY}
\bibliographystyle{unsrtnat}
 %\bibliographystyle{ieeetr}
 %\bibliographystyle{plainnat}
\bibliography{refs}
\end{ThesisBibliography}

 % ... vita ...

\begin{Vita}
Edward Norris graduated from Missouri University of Science and Technology in 2013 with a B.S. in both nuclear engineering and computer science, he is currently pursuing both a M.S. in computer science and a PhD in nuclear engineering. His PhD work is currently funded by a fellowship through the NRC. Edward was awarded the College of Engineering and Computing PhD Scholar award in 2017 for his academic achievements.

Previously he has participated in four summer internships at Sandia National Laboratories. While there, he served in various capacities ranging from cyber defense to radiation detection and neutron scatter simulation. He was largely involved with numerical simulations of radiation transport using Geant4 and MCNP6 as well as data collection.

Edward was also an active member of the Nuclear Science Design Team at Missouri University of Science and Technology. While on the team he solved radiation transport problems to facilitate the dosimetry of an inertial electrostatic confintement fusion device being constructed.


\end{Vita}

\end{document}

